Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-22 paper/main.tex
sheaf equation w/ object notation

\note{the notation here may need to be X and Y}

@@

 \begin{definition} A functor is a morphism between any two  categories $\bm{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}

@@

Over these open sets $\openset_i$ are sets of local sections

\begin{definition} \label{def:category:E} The category \mathcal{\dtotalc} is a subcategory of \textbf{Set} and consists of 
  \begin{itemize}
    \item \textit{objects} sets of sections $\Gamma(\openset_{j}, \dtotal)$ for all $U_j \subset \dtotal$
    \item \textit{morphisms}  $\iota^*: \Gamma(\openset_{k}, \dtotal) \hookrightarrow \Gamma(\openset_{j}, \dtotal)$ for all  $\openset_j, \openset_k \subset \dtotal$
  \end{itemize} 
\end{definition}

We model data as the sheaf $\sheafc_{\dtotalc}: \mathcal{\dbasec}^{op}\rightarrow \mathcal{\dtotalc}$
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \mathcal{\dtotalc} & \\
{} \arrow[rr, "\dfuncc", Rightarrow, shift right, shorten=3em] & & {} \\
    & \mathcal{\dbasec}^{op} \arrow[uu, "\sheafc_{\dtotalc}", bend left] \arrow[uu, "\sheafc_{\dtotalc}"', bend right] &   
\end{tikzcd}
\end{equation}
where the map \dfunc\ is any arbitrary function between sheafs. The sheaf $\sheaf_{\dtotal}$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf_{\mathcal{\dtotal}}|_{k}\coloneqq \lim\limits_{U\ni k} \Gamma(U, \dtotal)$ \cite{StalkSheaf2019}.

>>>>

@@

 \begin{definition} A functor is a morphism between objects of any two  categories $\bm{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}

@@

We model data as the sheaf $\sheafc({\dtotalc}): \mathcal{\dbasec}^{op}\rightarrow \bm{Set}$. The objects of \textbf{Set} in this sheaf are the sets of sections introduced in \autoref{eq:related-work:continuity:sections} and the morphisms are the inclusion maps in \autoref{eq:related-work:continuity:presheaf}. 
\begin{equation}
  \label{eq:artist:morphism-of-sheaf-data}
  \begin{tikzcd}
    & \Gamma(\opensetc_i, \dtotalc) \in Ob(\bm{Set}) & \\
{} \arrow[rr, "\dfuncc", Rightarrow, pos=.3, shorten <=3.5em, shorten >=8.85em] & & {} \\
    & \opensetc_i \in Ob(\mathcal{\dbasec}^{op}) \arrow[uu, "\sheafc(\dtotalc)", bend left, shift left = 10.5] \arrow[uu, "\sheafc(\dtotalc)"', bend right, shift left=10.5] &   
\end{tikzcd}
\end{equation}
 The map $\dfunc: \sheaf(\dtotal) \rightarrow \sheaf(\dtotal)$ is any arbitrary function between sheafs. The sheaf $\sheaf(\dtotal)$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk $\sheaf(\dtotal)|_{\dbasepoint}\coloneqq \lim\limits_{\openset\ni \dbasepoint} \Gamma(\openset, \dtotal)$ \cite{StalkSheaf2019}.
